An indexed construction of semi-simplicial and semi-cubical types

### 2022-06-01 paper/paper.tex
paper: eliminate use of patchcmd; still doesn't work
paper: inching closer and closer to xkv-patching
paper: some guesswork progress in xkv-patch
paper: XKV@delete doesn't seem to work; debugging
paper: major debugging in progress
xkv patch: debugging draws to an end!
paper: #2 is inaccessible in patched command
paper: down to very minor issues of specifying optarg
paper: Some syntax error from expansion?
paper: table beautification; mask disabled
paper: minor polish without breakage
paper: switch to xpatchcmd without breakage
paper: namespace within bonak family
paper: some more progress; ift

\usepackage{multirow, minted, tabularx, booktabs, setspace, makecell, caption, xkeyval, xstring, xpatch, pdflscape}
\usepackage[a4paper, inner=25mm, outer=25mm, top=25mm, bottom=25mm]{geometry}

% Some lua magic to join a variable number of arguments with commas
% Comma-separeated optional arguments
\begin{luacode*}
  function remove_empty(tbl)
    for i, v in ipairs(tbl) do
        if v == "" then
          table.remove(tbl, i)
          return remove_empty(tbl)
        end
    end
    return tbl
  end
  function join_with_comma(prefix, tbl)
    str = table.concat(remove_empty(tbl), ",")
    if str == "" then
      return str
    end
    return prefix .. str
  end
\end{luacode*}

\newcommandx{\joinargs}[6][2=,3=,4=,5=,6=]{\directlua{tex.sprint(join_with_comma("#1", {"\luaescapestring{#2}";"\luaescapestring{#3}";"\luaescapestring{#4}";"\luaescapestring{#5}";"\luaescapestring{#6}"}))}}

@@

% Universe, referred to as U
\newcommand{\U}[1]{\ensuremath{\mathsf{\color{spanish-blue}{U}}_{#1}}}

% The unit type
\newcommand{\unittype}{\ensuremath{\mathsf{unit}}}
\newcommand{\unitpoint}{\ensuremath{\star}}

% Definitional and extensional equality
\newcommand{\defeq}{\ensuremath{\triangleq}}
\newcommand{\eqHSet}{\ensuremath{\equiv_{\mathit{HSet}}}}
\newcommand{\reflHSet}{\ensuremath{\mathsf{refl}_{\mathit{HSet}}}}

% Magic with xkeyval to go over the 9-argument limit of LaTeX
\makeatletter
\define@cmdkey{X}{D}{(#1)}

\define@cmdkey[prim]{frame}{D}{(#1)}
\define@cmdkey[prim]{layer}{D}{(#1)}
\define@cmdkey[prim]{layer}{d}{(#1)}
\define@cmdkey[prim]{filler}{D}{(#1)}
\define@cmdkey[prim]{filler}{E}{(#1)}
\define@cmdkey[prim]{filler}{d}{(#1)}
\define@cmdkey[prim]{fullframe}{D}{(#1)}

\define@cmdkey[restr]{frame}{D}{(#1)}
\define@cmdkey[restr]{frame}{d}{(#1)}
\define@cmdkey[restr]{layer}{D}{(#1)}
\define@cmdkey[restr]{layer}{d}{(#1)}
\define@cmdkey[restr]{layer}{l}{(#1)}
\define@cmdkey[restr]{filler}{D}{(#1)}
\define@cmdkey[restr]{filler}{E}{(#1)}
\define@cmdkey[restr]{filler}{d}{(#1)}
\define@cmdkey[restr]{filler}{c}{(#1)}

\define@cmdkey[coh]{frame}{D}{(#1)}
\define@cmdkey[coh]{frame}{d}{(#1)}
\define@cmdkey[coh]{layer}{D}{(#1)}
\define@cmdkey[coh]{layer}{d}{(#1)}
\define@cmdkey[coh]{layer}{l}{(#1)}
\define@cmdkey[coh]{filler}{D}{(#1)}
\define@cmdkey[coh]{filler}{E}{(#1)}
\define@cmdkey[coh]{filler}{d}{(#1)}
\define@cmdkey[coh]{filler}{c}{(#1)}
\makeatother

% More magic: we patch xkeyval's \setkeys to use a mask to ignore keys
\makeatletter
% Our global mask
\def\bonak@mask{}
\def\bonak@na{}

% First we define \appendmask
\long\def\bonak@appendmask[#1]{
  \XKV@for@eo\XKV@fams\XKV@tfam{
    \def\bonak@hdr{\XKV@prefix\XKV@tfam @}
    \XKV@for@o{#1}\XKV@tempa{
      \XKV@addtolist@x\bonak@mask{\bonak@hdr\XKV@tempa}
    }
  }
}
\def\appendmask{\XKV@testopta{\XKV@testoptc\bonak@appendmask}}

% Now we patch \XKV@setkeys
\xpretocmd{\XKV@setkeys}{
  \XKV@for@eo\XKV@fams\XKV@tfam{
    \def\bonak@hdr{\XKV@prefix\XKV@tfam @}
    \XKV@for@eo{\bonak@mask}\XKV@tempa{
      \IfBeginWith{\XKV@tempa}{\bonak@hdr}{
        \def\XKV@tempb{\StrBehind{\XKV@tempa}{\bonak@hdr}}
        \XKV@addtolist@o\bonak@na{\XKV@tempb}}{}
    }
  }
}{\tracingpatches}{\tracingpatches}
\xpatchcmd{\XKV@setkeys}{#1}{\bonak@na}{\tracingpatches}{\tracingpatches}
\makeatother

% Truncated sets, otherwise referred to as X: the general macro
\newcommandx*{\X}[3][1=,2=,3=]{
  \ensuremath{\mathsf{\color{carolina}{X}}_{#1}^{#2}}
  \setkeys*{X}{#3}
}

% Frame, layer, and filler: the general macro
\newcommandx*{\prim}[6][2=,3=,4=,5=,6=]{
  \ensuremath{\mathsf{\color{indian-yellow}{#1}}_{#2}^{
    \joinargs{}[#3][#4][#5]}}
  \setkeys*[prim]{#1}{#6}
}

% Restriction for frame, layer, and filler: the general macro
\newcommandx*{\restr}[8][2=,3=,4=,5=,6=,7=,8=]{
  \ensuremath{\mathsf{\color{russian-green}{restr}}_{
    \mathsf{\color{indian-yellow}{#1}}
    \joinargs{,}[#2][#3][#4]}^{\joinargs{}[#5][#6][#7]}}
  \setkeys*[restr]{#1}{#8}
}

@@

% Hack: we'd like \coh to take 10 arguments, with the 10th being passed to
% xkeyval, but this is not possible. The only possible compromise is to join
% #7 and #8 by hand in usage of \coh: it's now #7 or '#6,#7' in \cohfoo commands
\newcommandx*{\coh}[9][2=,3=,4=,5=,6=,7=,8=,9=]{
  \ensuremath{\mathsf{\color{chestnut}{coh}}_{
    \mathsf{\color{indian-yellow}{#1}}
    \joinargs{,}[#2][#3][#4][#5][#6]}^{\joinargs{}[#7][#8]}}
  \setkeys*[coh]{#1}{#9}
}

% Some abbreviations
\newcommand{\imp}{\ensuremath{\rightarrow}}
\newcommand{\overright}[1]{\ensuremath{\overrightarrow{#1}}}
\renewcommand{\D}{\ensuremath{D}}
\newcommand{\hdD}{\ensuremath{D.1}}
\newcommand{\tlD}{\ensuremath{D.2}}
\renewcommand{\d}{\ensuremath{d}}
\newcommand{\E}{\ensuremath{E}}
\renewcommand{\l}{\ensuremath{l}}
\renewcommand{\c}{\ensuremath{c}}
\newcommand{\pair}[2]{\ensuremath{#1, #2}}

@@

% The eqntable environment, displaying the various
\NewDocumentEnvironment{eqntable}{m}{\table[H]\small\hrule\vspace{0.5em}
\tabularx{\textwidth}{@{} l c c >{\centering\arraybackslash}X @{}}}
{\endtabularx\vspace{0.3em}\hrule\vspace{0.5em}\caption{#1}\endtable}

% A block in the eqntable environment
\newcommand{\eqnline}[4]{$#1$ & $#2$ & $#3$ & $#4$ \\}
\newcommand{\mc}[1]{\multicolumn{4}{c}{\emph{#1}} \\\\}

@@

\begin{table}[H]
  \begin{tabularx}{\linewidth}{p{.3\linewidth}|p{.3\linewidth}|p{.3\linewidth}}
    \toprule
            & Set theory & Type theory \\
    \midrule
    Fibered & CCHM       &             \\
    \midrule
    Indexed &            & Our work    \\
    \bottomrule
  \end{tabularx}
\end{table}

@@

% Truncated sets, otherwise referred to as X
% Keep all arguments
\newcommandx{\Xp}[1]{\X[#1][]}
\newcommandx{\Xto}[2]{\X[#1][<#2]}
\newcommandx{\Xcomp}[2]{\X[#1][=#2]}
\newcommandx{\Xfrom}[2]{\X[#1][\geq#2]}

% Frame, layer, and filler
% Drop the universe letter
\newcommandx{\framep}[5][1=,2=,3=,4=,5=]{\prim{frame}[][#2][#3][#4][#5]}
\newcommandx{\layer}[5][1=,2=,3=,4=,5=]{\prim{layer}[][#2][#3][#4][#5]}
\newcommandx{\filler}[5][1=,2=,3=,4=,5=]{\prim{filler}[][#2][#3][#4][#5]}

% Restriction for frame, layer, and filler
% Drop the unviverse letter and q
\newcommandx{\restrf}[7][1=,2=,3=,4=,5=,6=,7=]{\restr{frame}[][#2][][#4][#5][#6][#7]}
\newcommandx{\restrl}[7][1=,2=,3=,4=,5=,6=,7=]{\restr{layer}[][#2][][#4][#5][#6][#7]}
\newcommandx{\restrc}[7][1=,2=,3=,4=,5=,6=,7=]{\restr{filler}[][#2][][#4][#5][#6][#7]}

% Coherence conditions for frame, layer, and filler
% Keep only ε, ω; n, p; proposition on n and p
\newcommandx{\cohf}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{frame}[][#2][#3][][][][][#9]}
\newcommandx{\cohl}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{layer}[][#2][#3][][][][][#9]}
\newcommandx{\cohc}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{filler}[][#2][#3][][][][][#9]}

@@

\input{tab-coind.tex}

% For just the second table, keep the universe letter in fullframe
\newcommandx{\fullframe}[3][1=,2=,3=]{\prim{fullframe}[#1][#2][][][#3]}
\input{tab-core.tex}

% Drop the universe letter in fullframe for all remaining tables
\renewcommandx{\fullframe}[3][1=,2=,3=]{\prim{fullframe}[][#2][][][#3]}
\input{tab-frames.tex}

% From the third table onwards, make the {D, E} arguments of prims implicit
\appendmask[prim]{frame}[D]
\appendmask[prim]{layer}[D]
\appendmask[prim]{filler}[D,E]

% Truncated sets, otherwise referred to as X
% Drop the universe letter for the third and fourth tables
\renewcommandx{\Xto}[2]{\X[][<#2]}
\renewcommandx{\Xcomp}[2]{\X[][=#2]}
\renewcommandx{\Xfrom}[2]{\X[][\geq#2]}

% The third table mentions cohframe; keep ε, ω in this instance
\renewcommandx{\cohf}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{frame}[][#2][#3][][][#6,#7][#8][#9]}
\input{tab-faces.tex}

% Restriction for frame, layer, and filler
% Drop just the universe letter for the coh table
\renewcommandx{\restrf}[7][1=,2=,3=,4=,5=,6=,7=]{\restr{frame}[][#2][#3][#4][#5][#6][#7]}
\renewcommandx{\restrl}[7][1=,2=,3=,4=,5=,6=,7=]{\restr{layer}[][#2][#3][#4][#5][#6][#7]}
\renewcommandx{\restrc}[7][1=,2=,3=,4=,5=,6=,7=]{\restr{filler}[][#2][#3][#4][#5][#6][#7]}

% Frame, layer, and filler
% Drop all arguments for coh table; they're not present in coind table.
\renewcommandx{\framep}[5][1=,2=,3=,4=,5=]{\prim{frame}[][][][][#5]}
\renewcommandx{\layer}[5][1=,2=,3=,4=,5=]{\prim{layer}[][][][][#5]}
\renewcommandx{\filler}[5][1=,2=,3=,4=,5=]{\prim{filler}[][][][][#5]}

% Coherence conditions for frame, layer, and filler
% Drop universe letter, ε, and ω
\renewcommandx{\cohf}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{frame}[][][][#4][#5][#6,#7][#8][#9]}
\renewcommandx{\cohl}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{layer}[][][][#4][#5][#6,#7][#8][#9]}
\renewcommandx{\cohc}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{filler}[][][][#4][#5][#6,#7][#8][#9]}
\input{tab-coh.tex}

@@

\newpage
\appendix
\section{Tables in full detail}
% Keep all arguments for all macros
% Frame, layer, and filler
\renewcommandx{\framep}[5][1=,2=,3=,4=,5=]{\prim{frame}[#1][#2][#3][#4][#5]}
\renewcommandx{\layer}[5][1=,2=,3=,4=,5=]{\prim{layer}[#1][#2][#3][#4][#5]}
\renewcommandx{\filler}[5][1=,2=,3=,4=,5=]{\prim{filler}[#1][#2][#3][#4][#5]}
\renewcommandx{\fullframe}[3][1=,2=,3=]{\prim{fullframe}[#1][#2][][][#3]}

% Restriction for frame, layer, and filler
\renewcommandx{\restrf}[7][1=,2=,3=,4=,5=,6=,7=]{\restr{frame}[#1][#2][#3][#4][#5][#6][#7]}
\renewcommandx{\restrl}[7][1=,2=,3=,4=,5=,6=,7=]{\restr{layer}[#1][#2][#3][#4][#5][#6][#7]}
\renewcommandx{\restrc}[7][1=,2=,3=,4=,5=,6=,7=]{\restr{filler}[#1][#2][#3][#4][#5][#6][#7]}

% Coherence conditions for frame, layer, and filler
\renewcommandx{\cohf}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{frame}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
\renewcommandx{\cohl}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{layer}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
\renewcommandx{\cohc}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{filler}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}

\input{tab-coind.tex}
\input{tab-core.tex}
\input{tab-frames.tex}

\begin{landscape}
  \input{tab-faces.tex}
  \input{tab-coh.tex}
\end{landscape}

>>>>

\usepackage{multirow, minted, tabularx, environ, booktabs, setspace, makecell, caption, xkeymask, joinargs, colortbl, pdflscape, ct, sset}
\usepackage[a4paper, inner=25mm, outer=25mm, top=25mm, bottom=25mm]{geometry}

@@

% Magic with xkeyval to go over the 9-argument limit of LaTeX
\makeatletter
\define@cmdkey[bonak]{X}{D}{(#1)}

\define@cmdkey[bonak]{frame}{D}{(#1)}
\define@cmdkey[bonak]{layer}{D}{(#1)}
\define@cmdkey[bonak]{layer}{d}{(#1)}
\define@cmdkey[bonak]{filler}{D}{(#1)}
\define@cmdkey[bonak]{filler}{E}{(#1)}
\define@cmdkey[bonak]{filler}{d}{(#1)}
\define@cmdkey[bonak]{fullframe}{D}{(#1)}

\define@cmdkey[bonak]{restrframe}{D}{(#1)}
\define@cmdkey[bonak]{restrframe}{d}{(#1)}
\define@cmdkey[bonak]{restrlayer}{D}{(#1)}
\define@cmdkey[bonak]{restrlayer}{d}{(#1)}
\define@cmdkey[bonak]{restrlayer}{l}{(#1)}
\define@cmdkey[bonak]{restrfiller}{D}{(#1)}
\define@cmdkey[bonak]{restrfiller}{E}{(#1)}
\define@cmdkey[bonak]{restrfiller}{d}{(#1)}
\define@cmdkey[bonak]{restrfiller}{c}{(#1)}

\define@cmdkey[bonak]{cohframe}{D}{(#1)}
\define@cmdkey[bonak]{cohframe}{d}{(#1)}
\define@cmdkey[bonak]{cohlayer}{D}{(#1)}
\define@cmdkey[bonak]{cohlayer}{d}{(#1)}
\define@cmdkey[bonak]{cohlayer}{l}{(#1)}
\define@cmdkey[bonak]{cohfiller}{D}{(#1)}
\define@cmdkey[bonak]{cohfiller}{E}{(#1)}
\define@cmdkey[bonak]{cohfiller}{d}{(#1)}
\define@cmdkey[bonak]{cohfiller}{c}{(#1)}
\makeatother

% Truncated sets, otherwise referred to as X: the general macro
\newcommandx{\X}[3][1,2,3]{
  \mathsf{\color{carolina}{X}}_{#1}^{#2}
  \setkeys*[bonak]{X}{#3}
}

% Frame, layer, and filler: the general macro
\newcommandx{\prim}[6][2,3,4,5,6]{
  \ensuremath{\mathsf{\color{indian-yellow}{#1}}_{#2}^{
    \joinargs{}[#3][#4][#5]}}
  \setkeys*[bonak]{#1}{#6}
}

% Restriction for frame, layer, and filler: the general macro
\newcommandx{\restr}[8][2,3,4,5,6,7,8]{
  \ensuremath{\mathsf{\color{russian-green}{restr}}_{
    \mathsf{\color{indian-yellow}{#1}}
    \joinargs{,}[#2][#3][#4]}^{\joinargs{}[#5][#6][#7]}}
  \setkeys*[bonak]{restr#1}{#8}
}

@@

% Hack: we'd like \coh to take 10 arguments, with the 10th being passed to
% xkeyval, but this is not possible. The only possible compromise is to join
% #7 and #8 by hand in usage of \coh: it's now #7 or '#6,#7' in \cohfoo commands
\newcommandx{\coh}[9][2,3,4,5,6,7,8,9]{
  \ensuremath{\mathsf{\color{chestnut}{coh}}_{
    \mathsf{\color{indian-yellow}{#1}}
    \joinargs{,}[#2][#3][#4][#5][#6]}^{\joinargs{}[#7][#8]}}
  \setkeys*[bonak]{coh#1}{#9}
}

% Universe, referred to as U
\newcommand{\U}[1]{\mathsf{\color{spanish-blue}{U}}_{#1}}

% The unit type
\newcommand{\unittype}{\mathsf{unit}}
\newcommand{\unitpoint}{\star}

% Definitional and extensional equality
\newcommand{\defeq}{\triangleq}
\newcommand{\eqHSet}{\ensuremath{\equiv_{\mathit{HSet}}}}
\newcommand{\reflHSet}{\ensuremath{\mathsf{refl}_{\mathit{HSet}}}}

% Some abbreviations
\newcommand{\imp}{\rightarrow}
\newcommand{\overright}[1]{\overrightarrow{#1}}
\renewcommand{\D}{D}
\newcommand{\hdD}{D.1}
\newcommand{\tlD}{D.2}
\renewcommand{\d}{d}
\newcommand{\E}{E}
\renewcommand{\l}{l}
\renewcommand{\c}{c}
\newcommand{\pair}[2]{#1, #2}

@@

% The eqntable environment, displaying the various
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\NewEnviron{eqntable}[1]{
  \begin{table}[H]
    \small
    \begin{tabularx}{\linewidth}{@{}>{$}l<{$} >{$}c<{$} >{$}c<{$} >{$}Y<{$} @{}}
      \toprule
      \BODY
      \bottomrule
    \end{tabularx}
    \caption{#1}
  \end{table}
}

% The label, since we're including twice
\newcommand*{\lab}{}

% \midrule color
\def\graymidrule{\arrayrulecolor{gray30}\midrule\arrayrulecolor{gray65}}

% A block in the eqntable environment
\NewDocumentCommand{\eqnline}{m m m m}{#1 & #2 & #3 & #4 \\}
\newcommandx*{\mc}[1]{\multicolumn{4}{c}{\emph{#1}} \\\\}

@@

\begin{table}[H]
  \begin{tabularx}{\linewidth}{p{.3\linewidth}|p{.3\linewidth}|p{.3\linewidth}}
    \toprule
            & Set theory & Type theory \\
    \graymidrule
    Fibered & CCHM       &             \\
    \graymidrule
    Indexed &            & Our work    \\
    \bottomrule
  \end{tabularx}
\end{table}

@@

% Truncated sets, otherwise referred to as X
% Keep all arguments
\newcommandx{\Xp}[1]{\X[#1][][]}
\newcommandx{\Xto}[3][3=]{\X[#1][<#2][#3]}
\newcommandx{\Xcomp}[3][3=]{\X[#1][=#2][#3]}
\newcommandx{\Xfrom}[3][3=]{\X[#1][\geq#2][#3]}

% Frame, layer, and filler
% Drop the universe letter
\newcommandx{\framep}[5][1,2,3,4,5]{\prim{frame}[][#2][#3][#4][#5]}
\newcommandx{\layer}[5][1,2,3,4,5]{\prim{layer}[][#2][#3][#4][#5]}
\newcommandx{\filler}[5][1,2,3,4,5]{\prim{filler}[][#2][#3][#4][#5]}

% Restriction for frame, layer, and filler
% Drop the unviverse letter and q
\newcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[][#2][][#4][#5][#6][#7]}
\newcommandx{\restrl}[7][1,2,3,4,5,6,7]{\restr{layer}[][#2][][#4][#5][#6][#7]}
\newcommandx{\restrc}[7][1,2,3,4,5,6,7]{\restr{filler}[][#2][][#4][#5][#6][#7]}

% Coherence conditions for frame, layer, and filler
% Keep only ε, ω; n, p; proposition on n and p
\newcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][][][][][#9]}
\newcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[][#2][#3][][][][][#9]}
\newcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{filler}[][#2][#3][][][][][#9]}

@@

\renewcommand*{\lab}{tab:coind}
\input{tab-coind.tex}

% For just the second table, keep the universe letter in fullframe
\newcommandx{\fullframe}[3][1,2,3]{\prim{fullframe}[#1][#2][][][#3]}
\renewcommand*{\lab}{tab:core}
\input{tab-core.tex}

% Drop the universe letter in fullframe for all remaining tables
\renewcommandx{\fullframe}[3][1,2,3]{\prim{fullframe}[][#2][][][#3]}
\renewcommand*{\lab}{tab:frames}
\input{tab-frames.tex}

% For the last two tables
\appendmask[bonak]{frame}[D]
\appendmask[bonak]{layer}[D]
\appendmask[bonak]{filler}[D, E]
\appendmask[bonak]{restrframe}[D]
\appendmask[bonak]{restrlayer}[D, d]
\appendmask[bonak]{restrfiller}[D, d]

% Truncated sets, otherwise referred to as X
% Drop the universe letter for the third and fourth tables
\renewcommandx{\Xto}[3][3]{\X[][<#2][#3]}
\renewcommandx{\Xcomp}[3][3]{\X[][=#2][#3]}
\renewcommandx{\Xfrom}[3][3]{\X[][\geq#2][#3]}

% The third table mentions cohframe; keep ε, ω in this instance
\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][][][#6,#7][#8][#9]}
\renewcommand*{\lab}{tab:faces}
\input{tab-faces.tex}

% For the last table,
% (1) make the {d} arguments of restr implicit
% (2) make the {D, E} arguments of coh implicit
\appendmask[bonak]{cohframe}[D]
\appendmask[bonak]{cohlayer}[D]
\appendmask[bonak]{cohfiller}[D, E]

% Restriction for frame, layer, and filler
% Drop just the universe letter for the coh table
\renewcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[][#2][#3][#4][#5][#6][#7]}
\renewcommandx{\restrl}[7][1,2,3,4,5,6,7]{\restr{layer}[][#2][#3][#4][#5][#6][#7]}
\renewcommandx{\restrc}[7][1,2,3,4,5,6,7]{\restr{filler}[][#2][#3][#4][#5][#6][#7]}

% Frame, layer, and filler
% Drop all arguments for coh table; they're not present in coind table.
\renewcommandx{\framep}[5][1,2,3,4,5]{\prim{frame}[][][][][#5]}
\renewcommandx{\layer}[5][1,2,3,4,5]{\prim{layer}[][][][][#5]}
\renewcommandx{\filler}[5][1,2,3,4,5]{\prim{filler}[][][][][#5]}

% Coherence conditions for frame, layer, and filler
% Drop universe letter, ε, and ω
\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][][][#4][#5][#6,#7][#8][#9]}
\renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[][][][#4][#5][#6,#7][#8][#9]}
\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{filler}[][][][#4][#5][#6,#7][#8][#9]}
\renewcommand*{\lab}{tab:coh}
\input{tab-coh.tex}

@@

\newpage
\appendix
\section{Tables in full detail}
% Clear the mask and label
\clearmask

% Keep all arguments for all macros
% Frame, layer, and filler
\renewcommandx{\framep}[5][1,2,3,4,5]{\prim{frame}[#1][#2][#3][#4][#5]}
\renewcommandx{\layer}[5][1,2,3,4,5]{\prim{layer}[#1][#2][#3][#4][#5]}
\renewcommandx{\filler}[5][1,2,3,4,5]{\prim{filler}[#1][#2][#3][#4][#5]}
\renewcommandx{\fullframe}[3][1,2,3]{\prim{fullframe}[#1][#2][][][#3]}

% Restriction for frame, layer, and filler
\renewcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[#1][#2][#3][#4][#5][#6][#7]}
\renewcommandx{\restrl}[7][1,2,3,4,5,6,7]{\restr{layer}[#1][#2][#3][#4][#5][#6][#7]}
\renewcommandx{\restrc}[7][1,2,3,4,5,6,7]{\restr{filler}[#1][#2][#3][#4][#5][#6][#7]}

% Coherence conditions for frame, layer, and filler
\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
\renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{filler}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}

\renewcommand*{\lab}{fulltab:coind}
\input{tab-coind.tex}
\renewcommand*{\lab}{fulltab:core}
\input{tab-core.tex}
\renewcommand*{\lab}{fulltab:frames}
\input{tab-frames.tex}

\begin{landscape}
  \renewcommand*{\lab}{fulltab:faces}
  \input{tab-faces.tex}
  \renewcommand*{\lab}{fulltab:coh}
  \input{tab-coh.tex}
\end{landscape}
